\pkg{Rgbp}: Bayesian Hierarchical Modeling and Frequentist Method Check

### 2013-04-17 jss/article.tex
adding school coverage pic

@@

\begin{CodeChunk}
\begin{CodeInput}
R> shr <- seq(0.01, 0.99, length.out = 20)
R> r.trial <- mean(n) * shr / (1 - shr)
R> cov.save <- sapply (1 : length(r.trial), function(i){
R>               coverage(b, A.or.r = r.trial[i], reg.coef = c(-1.194, 0.389), 
R>                        covariates = x1, nsim = 500)$average.coverageRB
R>             })
\end{CodeInput}
\end{CodeChunk}
\begin{figure}[h]
\begin{center}
\includegraphics[width = 5.5cm]{baseball4.png}
\end{center}
\end{figure}

>>>>

%\begin{CodeChunk}
%\begin{CodeInput}
%R> shr <- seq(0.01, 0.99, length.out = 20)
%R> A.trial <- mean(n) * (1 - shr) / shr
%R> cov.save <- sapply (1 : length(A.trial), function(i){
%R>               coverage(g, A.or.r = A.trial[i], reg.coef = 8.168, 
%R>                        nsim = 500)$average.coverageRB
%R>             })
%\end{CodeInput}
%\end{CodeChunk}
%\begin{figure}[h]
%\begin{center}
%\includegraphics[width = 5.5cm]{school3.png}
%\end{center}
%\end{figure}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> shr <- seq(0.01, 0.99, length.out = 20)
R> r.trial <- mean(n) * shr / (1 - shr)
R> cov.save <- sapply (1 : length(r.trial), function(i){
R>               coverage(b, A.or.r = r.trial[i], reg.coef = c(-1.194, 0.389), 
R>                        covariates = x, nsim = 500)$average.coverageRB
R>             })
\end{CodeInput}
\end{CodeChunk}
\begin{figure}[h]
\begin{center}
\includegraphics[width = 5.5cm]{baseball4.png}
\end{center}
\end{figure}
